%*******************************************************
% Publications
%*******************************************************
\pdfbookmark[2]{Publications}{publications}

\chapter{Publications list}

Most of the data presented in this thesis has been published in the following peer-reviewed articles:

\begin{itemize}
\item \textbf{Galardini, M.}, Mengoni, A., Brilli, M., Pini, F., Fioravanti, A., Lucas, S., Lapidus, A., et al. (2011). Exploring the symbiotic pangenome of the nitrogen-fixing bacterium \textit{Sinorhizobium meliloti}. BMC Genomics, 12(1), 235. BioMed Central Ltd. doi:10.1186/1471-2164-12-235
\item \textbf{Galardini, M.}, Biondi, E. G., Bazzicalupo, M., \& Mengoni, A. (2011). CONTIGuator: a bacterial genomes finishing tool for structural insights on draft genomes. Source code for biology and medicine, 6(1), 11. BioMed Central Ltd. doi:10.1186/1751-0473-6-11
\item Pini, F., \textbf{Galardini, M.}, Bazzicalupo, M., \& Mengoni, A. (2011). Plant-Bacteria Association and Symbiosis: Are There Common Genomic Traits in \textit{Alphaproteobacteria}?, Genes. 1017-1032. doi:10.3390 genes2041017
\item Peleg, A. Y., de Breij, A., Adams, M. D., Cerqueira, G. M., Mocali, S., \textbf{Galardini, M.}, Nibbering, P. H., et al. (2012). The Success of \textit{Acinetobacter} Species; Genetic, Metabolic and Virulence Attributes. (V. de Crécy-Lagard, Ed.)PLoS ONE, 7(10), e46984. doi:10.1371 / journal.pone.0046984
\end{itemize}

Submitted for publication

\begin{itemize}
\item \textbf{Galardini, M.}, Pini, F., Bazzicalupo, M., Biondi, E. G., Mengoni, M. Replicon-dependent bacterial genome evolution: the case of \textit{Sinorhizobium meliloti}. Sumitted to Genome Biology and Evolution.
\item Marco Fondi, Valerio Orlandini, Giorgio Corti, Marco Severgnini, \textbf{Marco Galardini}, Alessandro Pietrelli, Fabio Fuligni, Michele Iacono, Ermanno Rizzi, Gianluca De Bellis and Renato Fani. Enly: improving draft genomes through reads recycling. Submitted to Journal of Computational Biology.
\item Santopolo, L., Marchi, E., Decorosi, F., \textbf{Galardini, M.}, Brilli, M., Giovannetti, L., Viti, C. Draft Genome Sequence of Chromate-Resistant and Biofilm-Producing Strain \textit{Pseudomonas alcaliphila} 34. Submitted to Journal of Bacteriology.
\item \textbf{Galardini, M.}, Mengoni, M., Biondi, E. G., Florio, A., Bazzicalupo, M., Mocali, S. DuctApe: a tool for analysis and correlation of genomic and high throughput phenotypic data. Submitted to Bioinformatics.
\end{itemize}

Other articles in preparation related to this thesis

\begin{itemize}
\item Pini, F., Frage, B., Ferri, L., De Nisco, N., Taddei, L., Fioravanti, A., \textbf{Galardini, M.}, Brilli, M., Villeret, V., Bazzicalupo, M., Mengoni, A., Walker, G., Becker, A., Biondi, E. G. The cell cycle histidine kinase DivJ in \textit{Sinorhizobium meliloti} is essential for the symbiosis.
\item Pini, F., Spini, G., \textbf{Galardini, M.}, Bazzicalupo, M., Benedetti, A., Florio, A., Lagomarsino, A., Migliore, M., Mocali, S., Mengoni, A. Evolution and functional role of the putative nickel/H+ antiporter Sma1641 (nreB) in the symbiotic nitrogen fixer \textit{Sinorhizobium meliloti} Rm1021
\item \textbf{Galardini, M.}, Spini, G., Pini, F., Bazzicalupo, M., Biondi, E. G., Mengoni, M. Genome-wide analysis of symbiotic polymorphism in \textit{Sinorhizobium meliloti}.
\end{itemize}

The source files of this thesis will be available after the discussion as a git repository on \href{https://github.com/mgalardini/PhDGala}{GitHub} (@mgalardini).
